simon_test_loop

### 2019-03-20 src/stack_test.Rmd
minor mod
playing with random test data %

pre8.1 <- predict(mod8.1, test, args='outputformat=logistic' ) 
preplot8.1 <- plot(pre8.1)
preplot8.1

@@

maybe try enmval?

>>>>

pre8.1 <- predict(mod8.1, test, args=c('outputformat=logistic'), file="../output/maxtest.asc") # here i added an asc output so i could pop into arc for a test
preplot8.1 <- plot(pre8.1)
preplot8.1

@@

maybe try enmeval? NO CAN'T USE WITH SWD https://groups.google.com/forum/#!topic/maxent/lIT4tY_6toY
